A parallelised and distributed approach to implementing Conway's Game of Life

### 2022-12-06 report/article_2.tex
temp

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A parallelised and distributed approach to implementing Conway's Game of Life} % Article title
\author{%
\textsc{Aaron Chan}\\[1ex] % Your name
\normalsize University of Bristol \\ % Your institution
\normalsize {ho21739@bristol.ac.uk} % Your email address
\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
\textsc{Ferdinand Hubbard}\\[1ex] % Second author's name
\normalsize University of Bristol \\ % Your institution
\normalsize {ej21378@bristol.ac.uk} % Your email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{
\begin{abstract}
  We intend to explain our two solutions for implementing Conway's Game of Life in Golang, namely the Parallel and Distributed versions.
  Within this report, we will discuss the impacts of thread usage in both our implementations, as well as the effect of distributed computation as opposed to single-machine computation. In essence, we found that execution time was sped up as we increased thread count, reduced branch instructions and implemented a halo exchange mechanism.
\end{abstract}
}

@@

>>>>

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A parallelised and distributed approach to implementing Conway's Game of Life} % Article title
\author{%
\textsc{Aaron Chan}\\[1ex] % Your name
\normalsize University of Bristol \\ % Your institution
\normalsize {ho21739@bristol.ac.uk} % Your email address
\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
\textsc{Ferdinand Hubbard}\\[1ex] % Second author's name
\normalsize University of Bristol \\ % Your institution
\normalsize {ej21378@bristol.ac.uk} % Your email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{
\begin{abstract}
  We intend to explain our two solutions for implementing Conway's Game of Life in Golang, namely the Parallel and Distributed versions.
  Within this report, we will discuss the impacts of thread usage in the parallel implementation, as well as the effect of distributed computation as opposed to single-machine computation. In essence, we found that execution time was sped up as we increased thread count, reduced branch instructions and implemented a halo exchange mechanism.
\end{abstract}
}

@@

\begin{algorithm}
  \caption{modulo getNeighbourCount function}
  \begin{algorithmic}
    \State Let $row \gets rowCoordinate \% ImageHeight$
    \State Let $col \gets colCoordinate \% ImageWidth
    \If{row || col < 0}

    \EndIf

  %   \State Let $i, j \gets (row, column)$ on world
  % \State Let $O \gets [\{-1,0,1\} \times \{-1, 0, 1\} - \{0,0\}]$
  % \State Let $alive \gets 0$   
  % \For{$(x,y) \in O$}
  %     \State $row \gets (i + y)$
  %     \If{row < 0}
  %       \State $row \gets ImageHeight-1$
  %     \ElsIf{row = ImageHeight}
  %       \State $row \gets 0$
  %     \EndIf
  %     \State $col \gets (j + x)$
  %     \If{col < 0}
  %       \State $col \gets ImageWidth - 1$
  %       \ElsIf{col = ImageWidth}
  %         \State $col \gets 0$
  %     \EndIf
  %     \If{world[row][col] = 255}
  %     \State $alive++$
  %     \EndIf
  %   \EndFor
  %   \State \Return $alive$
  \end{algorithmic}
\end{algorithm}
